\documentclass[
    NAME={Dr. Helga Ingimundardóttir},
    EMAIL={helgaingim@hi.is},
    FACULTY={Industrial Engineering},
    TITLE={Designing Authentic Industry-Engaged Assessment for Professional Competence in Business Intelligence},
    SHORTTITLE={helgaingim CDIO: BI redesign},
    SEMINAR={22\textsuperscript{nd} International CDIO Conference},
    DATE={June 22\textsuperscript{nd} 2026},
    WIDE=true
]{HI-LaTeX/hi-beamer}
%\setbeameroption{show notes on second screen}
\usepackage{tikz}
\usetikzlibrary{fit,matrix,backgrounds}
\usepackage[fixed,style=solid]{fontawesome7}

\begin{document}

\section{Background}
% 1. Motivation & 2. Motivating case
\input{slides/motivation}
% 3. Context: Business Intelligence course
\input{slides/context}
% 4. Industry-engaged project
\input{slides/industry}

\section{Design approach and structure}
% 5. Design approach & 6. Pedagogical structure 
\input{slides/louis}

\section{Expectations and feedback}
% 7. Core mechanism: assessment as development
\input{slides/assessment}
% 8. Accumulated feedback & 9. Feedback structure
\input{slides/feedback}

\section{Findings}
% 10. Credibility and trust
\input{slides/trust}
% 11. Balancing team and individual assessment
\input{slides/teamvsindividual}
% 12. Evidence (indicative)
\input{slides/evidence}
% 13. Key tensions
\input{slides/tension}

\section{Summary}
% 14. Design principles
\input{slides/summary}
% 15. Limitations and future directions
\input{slides/futurework}
% 17. Questions
\input{slides/final}
\note{
This brings us back to the original problem.  

The issue was not student ability --  
it was that the work was not credible or usable in context.  

What this case shows  
is that professional competence does not emerge by itself.  

It requires making expectations explicit --  
especially around credibility, trust, and use.  

Assessment and feedback are the mechanisms that make this visible.  

When feedback accumulates,  
and when students must respond to different audiences,  
they begin to align their work with real practice.  

So the contribution is not a specific tool or method.  

It is showing how assessment and feedback  
can be used to align learning  
with professional expectations.
}
\end{document}

