\begin{frame}{Design focus: LOUIS-guided}
\begin{columns}[T,onlytextwidth]
\begin{column}{.35\textwidth}
\begin{alertblock}{\faKey~Design focus}
\begin{itemize}
    \item limited set of competences (LOUIS)
    \item sustained industry context
    \item iterative development toward capstone
\end{itemize}
\end{alertblock}
\end{column}

\begin{column}{.61\textwidth}

\begin{block}{LOUIS framework}
\small
\textbf{Learning Outcomes in University for Impact on Society}

Focus on a small set of competences (max 3)

\end{block}
\vspace{0.3em}

\centering
\resizebox{\linewidth}{!}{\input{include/LCF-tikz-en}}

\end{column}
\end{columns}
\end{frame}
\note{
For this redesign, I attended a workshop on the LOUIS framework --  
\emph{Learning Outcomes in University for Impact on Society}.  

LOUIS is part of the Aurora University Network,
and is intended to strengthen broader academic and personal competences  
alongside subject knowledge.  

A key takeaway from that workshop was to avoid spreading too thin --  
instead, focus on a \emph{small number of competences}  
and make expectations explicit.  

So this redesign is directly informed by that work.  

LOUIS helped translate high-level competence goals  
into concrete learning outcomes  
that students can understand and act on.  

}
\begin{frame}{Pedagogical structure}
\centering\resizebox{.8\linewidth}{!}{\input{include/course-flow-en}}
\begin{columns}[T,onlytextwidth]
    \begin{column}{.45\textwidth}
        \begin{itemize}
            \item[\faUserPlus] Team-Based Learning (TBL):
            \begin{itemize}
                \item[\faUser] iRAT (individual readiness)
                \item[\faUsers] tRAT (team readiness)
                \item[\faUsers] tAPP (team application)
                \item[\faUser] iREF (individual reflection)
            \end{itemize}
        \end{itemize}        
    \end{column}
    \begin{column}{.55\textwidth}
        \begin{itemize}            
            \item[\faShuffle] Flipped classroom
            \item[\faRepeat] Iterative modules leading into capstone
        \end{itemize}                
    \end{column}
\end{columns}
\end{frame}
\note{
The course combines \emph{TBL} with \emph{iterative} project work via \emph{PBL}  

Students prepare individually before class,  
and class time is used for discussion and guided project work.  (flipped classroom)

If we translate this into an Agile perspective:  
\begin{itemize}
    \item The preparation and initial team phase  
function like \emph{sprint planning}.  
    \item The subsequent sessions correspond to the \emph{sprint itself},  
where teams develop and refine their work.  
    \item And the individual reflection acts as a \emph{retrospective},  
capturing what should be improved next.  
    \item The capstone then brings this together.  
Rather than starting a new cycle,  
students revisit and refine previous work --  
which is closer to what in Agile would be called  
\emph{iteration on an evolving product}, not isolated sprints.  

    \item The final course reflection then acts as a broader retrospective.

\end{itemize}
}
